Refinements for open automata

### 2022-06-22 2021-Refinement/paper/refinementarticle.tex
proof thm1, thm2 and debut thm3

\item  Finally, we have to prove the following holds:
\begin{multline*}
\forall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{13}\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_3} \beta_{1j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
 R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}
\end{multline*}
According to the refinement relation between  $A_1$ and $A_2$ we have:
\begin{multline*}
\forall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
\end{multline*}
Yet according to the relation between   $A_2$ and $A_3$ we have:

\begin{multline*}
\forall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{1 x}\land
 R_{23}\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
\end{multline*}

For each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $. 
We can make the conjunction of these two formulas,
we get  $\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$  
\begin{multline*}
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X}, \bigsymb{\bigexists} 
\mpar{t_{2x} = \OTx{2}{y}{2y}{2y} \in \fOT{s_2}}^{y \in Y},\\
 V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \uplus \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \biguplus_{y\in Y}\fvars{t_{2y}}   \vdash \hspace{6cm}\\  \mpar{R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2} \wedge \mpar{ R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 }
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j}} 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}} \wedge\\
\bigsymb{\bigwedge_{y\in Y}}
\mpar{
\alpha_2=\alpha_{2 y}  \land J'_{2y}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2yj}\land g_{1 y}\land
 R_{23}\mpar{s'_{2 y}, s'_3}\psubst{\psi_{2 y} \uplus \psi_3}}\\
\end{multline*}

Note that if  either $R_{12}\mpar{s_1, s_2}$ or $R_{23}\mpar{s_2, s_3}$ is false the statement trivially holds.

By rearranging and simplifying we get:$\forall \mpar{s_1,s_2,s_3} \in S_1\times S_2 \times S_3$, $ \bigsymb{\forall} \mpar{t_1,t_2, t_{3}}\!=\! \\\mpar{\OTx{1}{}{1}{1},\OTx{2}{}{2}{2},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times\fOT{s_2} \times \fOT{s_3}$\\

\TODO{Manque Argument de simplification mecanique a trouver}
By removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.

@@

\begin{multline*}
\forall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
\bigsymb{\bigexists} 
\mpar{t_{13x} = \OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X},\\
 V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
 \alpha_{13}=\alpha_{1 3x} \land
J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
\end{multline*}

We pick $s_{13}$, $s'_{13a}$, and two open transitions $t_{13}$ and $t_{23}$.
Where $s_{13}=(s_1,s_3)$ and $s_{23}=(s_2,s_3)$ by construction of $R$.

@@

$\bullet$ if  the hole $k$ of A1 is not involved in the transition:
$t_1=\OTx{1}{}{1}{1}$ when  $k \not\in J'_{1} $
and 
\[
t_{13} = \OT{\mpar{s_1, s_3}}{\mpar{s'_1, {s_3}}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
\]

@@

Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_1$ and compose it with $t_3^2$.
We obtain 
\[
t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x} 
\]

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
\end{multline*}
Furthermore, from the property ($\star$) and from the definition of $t_{13x}'$:
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\Big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
  \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\\
 \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
 \end{multline*}
 \TODO{to check $j \in J'_2 \setminus\{k\}$}

@@

\item   It remains to prove the  satisfaction of the relation is preserved along identical transitions, i.e. the following is satisfied (we define $V_{12} = V_1 \uplus V_2$ and $ V_{23} = V_2\uplus V_3$):
\begin{multline*}
\forall \mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}, \bigsymb{\forall} \mpar{t_{12}, t_{13}} = \mpar{\OTx{12}{}{12}{12}, \OTx{13}{}{13}{13}} \in \fOT{s_{12}} \times \fOT{s_{13}} \\ 
\bigsymb{\bigexists} 
\mpar{t_{12x} = \OTx{12}{x}{12x}{12x} \in \fOT{s_{12}}}^{x \in X},\\
 V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
\vdash \hspace{6cm}\\  R\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
\implies \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
 \alpha_{12}=\alpha_{12x} \land
J'_{12x}  = J'_{13}  \land \bigwedge_\subbox{j \in  J'_{13}} \beta_{13j} = \beta_{12xj}\land g_{12x} \land
 R\mpar{s'_{12x}, s'_{13}}\psubst{\psi_{12x} \uplus \psi_{13}}}
\end{multline*}

-----------------------------------------------------

>>>>

\item  Finally, we have to prove the following holds:
\begin{multline*}
\bigforall \mpar{s_1, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_1, t_3} = \mpar{\OTx{1}{}{1}{1}, \OTx{3}{}{3}{3}} \in \fOT{s_1} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_3} \vdash \hspace{6cm}\\  R_{13}\mpar{s_1, s_3} \wedge 	g_1 \wedge g_3 \wedge \alpha_1 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_3} \beta_{1j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{1xj}\land g_{1 x}\land
 R_{13}\mpar{s'_{1 x}, s'_3}\psubst{\psi_{1 x} \uplus \psi_3}}
\end{multline*}
Firstly, according to the refinement relation between  $A_1$ and $A_2$ we have:
\begin{multline*}
\bigforall \mpar{s_1, s_2} \in S_1 \times S_2, \bigsymb{\forall} \mpar{t_1, t_2} = \mpar{\OTx{1}{}{1}{1}, \OTx{2}{}{2}{2}} \in \fOT{s_1} \times \fOT{s_2} \\ 
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},
 V_1 \uplus V_2 \uplus \biguplus_{x\in X}\fvars{t_{1x}} \uplus \fvars{t_1} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge 	g_1 \wedge g_2 \wedge \alpha_1 = \alpha_2 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}}
\end{multline*}
Yet according to the relation between   $A_2$ and $A_3$ we have:

\begin{multline*}
\bigforall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2 x}\land
 R_{23}\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
\end{multline*}

Note that if  either $R_{12}\mpar{s_1, s_2}$ or $R_{23}\mpar{s_2, s_3}$ is false the statement trivially holds.
So for each $s_2 \in S_2$, we remark that  $s_2$  allows to relate $s_1$ and $s_3$ if and only if $R_{12}\mpar{s_1, s_2}\land R_{23}\mpar{s_2, s_3} $. We pick a state $s_2$ relating both,  we can then the following be inferred from the above formulas:
$\forall \mpar{s_1,s_3} \in S_1 \times S_3$ and\\ $\bigsymb{\forall} \mpar{t_1, t_{3}}\!=\! \mpar{\OTx{1}{}{1}{1},\OTx{3}{}{3}{3}}\! \in\! \fOT{s_1} \times \fOT{s_3}$  
\begin{multline*}
\bigsymb{\bigexists} 
\mpar{t_{1x} = \OTx{1}{x}{1x}{1x} \in \fOT{s_1}}^{x \in X},\\
 V_1 \uplus V_2 \uplus V_3 \uplus \fvars{t_1} \uplus \fvars{t_2} \uplus \fvars{t_3} \uplus \biguplus_{x\in X}\fvars{t_{1x}}     \vdash \hspace{6cm}\\  R_{12}\mpar{s_1, s_2} \wedge R_{23}\mpar{s_2, s_3} \wedge 	g_1 \wedge g_2 \wedge   g_3\wedge  \alpha_1 = \alpha_2  \wedge \alpha_2 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j}} 
%\wedge \bigwedge_\subbox{j \in J'_1 \cap J'_2} \beta_{1j} = \beta_{2j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_1}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_1=\alpha_{1 x}  \land J'_{1x}= J'_2 \land \bigwedge_\subbox{j \in J'_2 } \beta_{2j} = \beta_{1xj}\land g_{1 x}\land
 R_{12}\mpar{s'_{1 x}, s'_2}\psubst{\psi_{1 x} \uplus \psi_2}} \wedge\\ R_{23}\mpar{s'_{2}, s'_3}\psubst{\psi_{2} \uplus \psi_3}\hspace{6cm}\\
\end{multline*}
By rearranging, simplifying and removing the variables of $A_2$ that have not effect on   $A_1$ et  $A_3$, we get the desired result.

@@

\begin{multline*}
\bigforall \mpar{s_{13}, s_{23}} \in S_{13} \times S_{23}, \bigsymb{\forall} \mpar{t_{13}, t_{23}} = \mpar{\OTx{13}{}{13}{13}, \OTx{23}{}{23}{23}} \in \fOT{s_{13}} \times \fOT{s_{23}} \\ 
\bigsymb{\bigexists} 
\mpar{t_{13x} = \OTx{13}{x}{13x}{13x} \in \fOT{s_{13}}}^{x \in X},\\
 V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
 \alpha_{13}=\alpha_{1 3x} \land
J'_{13x}  = J'_{23}  \land \bigwedge_\subbox{j \in  J'_{23}} \beta_{23j} = \beta_{13xj}\land g_{1 3x} \land
 R\mpar{s'_{1 3x}, s'_{23}}\psubst{\psi_{1 3x} \uplus \psi_{23}}}
\end{multline*}

We pick $s_{13}$, $s'_{13a}$, and two open transitions $t_{13}$ and $t_{23}$.
Where $s_{13}=(s_1,s_3)$ and $s_{23}=(s_2,s_3)$ by construction of $R'$.

@@

@@

Consider one $t_{1x}=\OT{s_1}{s_{1x}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x}}}{g_{1x}}{\psi_{1x}}\in \fOT{s_1}$ to obtain a new open transition of $A_{13}$ and compose it with $t_3^2$.
We obtain 
\[
t_{13x}' = \OT{\mpar{s_1, s_3}}{\mpar{s_{1x}, {s_3}}}{\alpha_{1x}}{\beta_{1xj}^{j \in J'_{1x} \setminus \{k\}} \uplus  {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{1x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{1xk}}{\psi_{1x} \uplus \psi^2_3} \qquad \text{ where } k \in J'_{1x} 
\]

This specifies the family $\mpar{t_{13x}'}^{x\in X}$
that allows us to prove the initial goal, i.e. the relation is preserved along identical transitions. We derive  from the definition of  $t_{23}$
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies \\
 R\mpar{s_{1}, s_{2}} \wedge 	g_{1} \wedge g_2 \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} \wedge \alpha_{1} = \alpha_{2} \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
\end{multline*}
Furthermore, from the property ($\star$) and from the definition of $t_{13x}'$:
\begin{multline*}
  V_{13} \uplus V_{23} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{13}} \uplus \fvars{t_{23}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{13}, s_{23}} \wedge 	g_{13} \wedge g_{23} \wedge \alpha_{13} = \alpha_{23} 
\implies 
\bigwedge_{x\in X}
\Big(
 \alpha_{13}=\alpha_1=\alpha_{1 x}  \land J'_{1x}\uplus J'_3= J'_2\uplus J'_3\land \\
  \bigwedge_\subbox{j \in J'_2 \setminus\{k\} } \beta_{2j} = \beta_{1xj}
 \land \bigwedge_\subbox{j \in {j \in J^{2 \prime}_3} }  (\beta^1_{3j}) = (\beta^2_{3j}) \land g_{1 x}\land
 R\mpar{s'_{1x}, s'_{2}}\psubst{\psi_{1 x} \uplus \psi_2}\Big) \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2k} = \beta_{1xk}\\
 \wedge \bigwedge_\subbox{v_3\in V_3}
 v^1_3=v^2_3\wedge s^1_3 = s^2_3
 \end{multline*}
 \TODO{to check why $j \in J'_2 \setminus\{k\}$}

@@

\item   It remains to prove the  satisfaction of the relation is preserved along identical transitions, i.e. the following is satisfied (we define $V_{12} = V_1 \uplus V_2$ and $ V_{23} = V_2\uplus V_3$):
\begin{multline*}
\forall \mpar{s_{12}, s_{13}} \in S_{12} \times S_{13}, \bigsymb{\forall} \mpar{t_{12}, t_{13}} = \mpar{\OTx{12}{}{12}{12}, \OTx{13}{}{13}{13}} \in \fOT{s_{12}} \times \fOT{s_{13}} \\ 
\bigsymb{\bigexists} 
\mpar{t_{12x} = \OTx{12}{x}{12x}{12x} \in \fOT{s_{12}}}^{x \in X},\\
 V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{1x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
\implies \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
 \alpha_{12}=\alpha_{12x} \land
J'_{12x}  = J'_{13}  \land \bigwedge_\subbox{j \in  J'_{13}} \beta_{13j} = \beta_{12xj}\land g_{12x} \land
 R'\mpar{s'_{12x}, s'_{13}}\psubst{\psi_{12x} \uplus \psi_{13}}}
\end{multline*}

We pick $s_{12}$, $s'_{12a}$, and two open transitions $t_{12}$ and $t_{13}$.
Where $s_{12}=(s_1,s_2)$ and $s_{13}=(s_1,s_3)$ by construction of $R'$.

We reason on the way the OT $t_{13}$ has been obtained: either the hole $k$ of $A_1$ is involved in the transition or not.

\paragraph{First case: Both $A_1$ and $A_3$ are involved in transition $t_{13}$.}
The transition $t_{13}$  is obtained  by the composition of transitions $t_3=\OTx{3}{}{3}{3}$ and  \[t_1^1=
\OT{ s^1_1}{{s^1_1}'}{\alpha_1^1}{   {(\beta^1_{1j})^{j \in J^{1 \prime}_1} }}{ g^1_1 }{ \psi^1_1} \qquad \text{ when } k \in {J^1_{1}}^{\prime}
\]
The result is the transition:
\[
t_{13} = \OT{\mpar{s^1_1, s_3}}{\mpar{{s^1_1}',s'_3 }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{3j})^{j \in J^{\prime}_3} }}{g^1_1 \wedge g_3 \wedge \alpha_3 = \beta^1_{1k}}{\psi^1_1 \uplus \psi_3} \qquad \text{ where } k \in {J^1_{1}}^{\prime} 
\]

According to the refinement relation between  $A_2$ and $A_3$ we have the following property that we denote $(*)$:
\begin{multline*}
\bigforall \mpar{s_2, s_3} \in S_1 \times S_3, \bigsymb{\forall} \mpar{t_2, t_3} = \mpar{\OTx{2}{}{2}{2}, \OTx{3}{}{3}{3}} \in \fOT{s_2} \times \fOT{s_3} \\ 
\bigsymb{\bigexists} 
\mpar{t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}}^{x \in X},
V_2 \uplus V_3\uplus \biguplus_{x\in X}\fvars{t_{2x}} \uplus \fvars{t_3} \uplus \fvars{t_2} \vdash \hspace{6cm}\\  R_{23}\mpar{s_2, s_3} \wedge 	g_2 \wedge g_3 \wedge \alpha_2 = \alpha_3 
%\wedge \bigwedge_\subbox{j \in J'_2 \cap J'_3} \beta_{2j} = \beta_{3j} 
\implies \hspace{6cm}\\
%\exists
%\OTx{1}{a}{3}{3}\in \fOT{s_2}. \\
\bigsymb{\bigwedge_{x\in X}}
\mpar{
\alpha_2=\alpha_{2 x}  \land J'_{2x}= J'_3 \land \bigwedge_\subbox{j \in J'_3 } \beta_{3j} = \beta_{2xj}\land g_{2 x}\land
 R\mpar{s'_{2 x}, s'_3}\psubst{\psi_{2 x} \uplus \psi_3}}\\
\end{multline*}
From the

Consider any transition $t_{2x} = \OTx{2}{x}{2x}{2x} \in \fOT{s_2}$ and compose it with  $t^1_1$. We get a family of  transitions:
\[
t_{12x}^{x\in X} = \mpar{\OT{\mpar{s^1_1, s_{2x}}}{\mpar{{s^1_1}',s'_{2x} }}{\alpha^1_1}{{\beta^1_{1j}}^{j \in J^{1 \prime}_1 \setminus \{k\}} \uplus  {(\beta_{2xj})^{j \in J^{\prime}_{2x}} }}{g^1_1 \wedge g_{2x} \wedge \alpha_{2x} = \beta^1_{1k}}{\psi^1_1 \uplus \psi_{2x}}}^{x\in X}  \quad \text{where } k \in {J^1_{1}}^{\prime}
\]
In order to prove the goal of of the expected relation let us start with the hypothesis:
\begin{multline*}
V_{12} \uplus V_{13} \uplus  \biguplus_{x\in X}\fvars{t_{2x}}  \uplus \fvars{t_{12}} \uplus \fvars{t_{13}} 
\vdash \hspace{6cm}\\  R'\mpar{s_{12}, s_{13}} \wedge 	g_{12} \wedge g_{13} \wedge \alpha_{12} = \alpha_{13} 
\implies  R\mpar{s_{2}, s_{3}}\wedge \bigwedge_\subbox{v_1\in V_1}\!\! v^1_1=v^2_1 \wedge s^1_1 = s^2_1 \wedge \\
g_1\wedge g^1_1 \wedge g_3 \wedge \alpha_3 = \beta^1_{1k} \wedge \alpha_2 = \alpha_3
\end{multline*}
From the property $(*)$ we get:

\newpage
